Return Oriented Programming

### 2023-02-15 paper.tex
changes

%%%% 2. PACKAGES %%%%
\usepackage{lipsum} % Example package -- can be removed
\usepackage{blt}
\usepackage{tabularx}
\usepackage{url}

@@

\section{Theory}
\subsection{Stack}
\subsection{ROP Chain}
\section{Attack}
\subsection{Target Program}
\paragraph{Target Program}
The following program is the target of our attack, it uses a command line argument to provide the payload and \Verb+strcpy+ for the buffer overflow, overwriting the return address after the 8 Byte buffer. Using vulnerable input functions also works though.
\bltCode{vuln.c}{c}{The Target Program}{thetargetprogram}

@@

\paragraph{struct.pack}
\Verb+struct.pack+ is a Python function that allows to easily generate our desired payload from the raw bytes. Bash then allows to directly pipe the generated payload into our target. In order to generate the payload we first have to fill the buffer and override the EBP with arbitary values as seen in line 2~\cref{howtopack}. This is usually done using easily recognizable characters, using the letter \Verb+A+ for this is common. It has the hex value \Verb+0x41+, doing this allows then to spot the buffer in a debugger like \Verb+gdb+. So in this example we fill the buffer with 8 \Verb+A+'s and 4 \Verb+B+'s. After that it is time to insert the addresses of the gadgets and the arguments. This is done by calling pack with the double word (64 Bit) while specifying the endianness, converting that to a string and adding it to the string as seen in line 3~\cref{howtopack}. After the whole payload has been generated we can print it and use the output directly for running the buffer overflow attack as mentioned above.
\bltCode{pack.py}{python}{How to use struct.pack}{howtopack}
\section{Results}

\section{Protection}

\section{Discussion}

%%%% 8. BILBIOGRAPHY %%%%
\bibliographystyle{alpha}
\bibliography{abbrev3,crypto,biblio}
%%%% NOTES
% - Download abbrev3.bib and crypto.bib from https://cryptobib.di.ens.fr/
% - Use bilbio.bib for additional references not in the cryptobib database.
%   If possible, take them from DBLP.

\end{document}

>>>>

%%%% 2. PACKAGES %%%%
\usepackage{lipsum} % Example package -- can be removed
\usepackage{blt}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{url}

@@

\section{Theory}
\subsection{Stack}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.65\textwidth]{stackropoffsec.png}
  \caption{The stack when injecting the payload}
  \label{fig:mesh1}
\end{figure}
\subsection{ROP Chain}

\section{Attack}
\label{sec:attack}
\subsection{Target Program}
\paragraph{Target Program}
The following program is the target of our attack, it uses a command line argument to provide the payload and \Verb+strcpy+ for the buffer overflow, overwriting the return address after the 8 Byte buffer. Using vulnerable input functions also works though.
\bltCode{vuln.c}{c}{The Target Program}{thetargetprogram}

@@

\paragraph{struct.pack}
\Verb+struct.pack+ is a Python function that allows to easily generate our desired payload from the raw bytes. Bash then allows to directly pipe the generated payload into our target. In order to generate the payload we first have to fill the buffer and override the EBP with arbitary values as seen in line 2~\cref{howtopack}. This is usually done using easily recognizable characters, using the letter \Verb+A+ for this is common. It has the hex value \Verb+0x41+, doing this allows then to spot the buffer in a debugger like \Verb+gdb+. So in this example we fill the buffer with 8 \Verb+A+'s and 4 \Verb+B+'s. After that it is time to insert the addresses of the gadgets and the arguments. This is done by calling pack with the double word (64 Bit) while specifying the endianness, converting that to a string and adding it to the string as seen in line 3~\cref{howtopack}. After the whole payload has been generated we can print it and use the output directly for running the buffer overflow attack as mentioned above.
\bltCode{pack.py}{python}{How to use struct.pack}{howtopack}
\section{Results}
\paragraph{Attack}
After injecting the generated payload from \cref{sec:attack} as a command line argument the program opened a shell from which we can use privilege escalation techniques in order to completely compromise the system. The only compiler options that had to be activated were PIE and stack canaries. It is likely that there are systems still in use today which are vulnerable to this kind of attack. Since it allows almost arbitrary code execution it is very important to identify these devices and patch or replace them.
\paragraph{ASLR}
The information about wether or not ROP can be applied to systems with ASLR enabled is inconsistent. In the run with PIE and stack canaries disabled the attack still worked even with \Verb+/proc/sys/kernel/randomize_va_space+ set to \Verb+2+, meaning full randomization of the different segments like header, libraries and stack. This is probably
\section{Protection}
Luckily we had to disable several security mechanisms to make this attack possible, especially

\section{Discussion}
Sources:
https://www.exploit-db.com/docs/english/28479-return-oriented-programming-(rop-ftw).pdf
%%%% 8. BILBIOGRAPHY %%%%
\bibliographystyle{alpha}
\bibliography{abbrev3,crypto,biblio}
%%%% NOTES
% - Download abbrev3.bib and crypto.bib from https://cryptobib.di.ens.fr/
% - Use bilbio.bib for additional references not in the cryptobib database.
%   If possible, take them from DBLP.
\end{document}
